### 2025-01-18 skripsi/chapter2.tex
add outline to ch1
add literature map

% !TEX root = ./skripsi.tex
\chapter{LITERATURE REVIEW}
\noindent This chapter will discuss and summarize the literature related to this study. The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field.
% \noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan. Judul bab tidak harus seperti yang dituliskan, melainkan dapat lebih fleksibel yang mencerminkan isi paparan pada bab ini. Demikian halnya dengan judul sub bab.

\section{Governing Equations}
\noindent Mathematical expressions that describe the behavior of a system are called governing equations. Typically, governing equations are in the form of Differential Equations (DE). For some systems with several variables, the governing equations are Partial Differential Equations (PDE). These equations are the foundation of many engineering and scientific models \autocite{olverIntroductionPartialDifferential2014,andersonGoverningEquationsFluid1992}. In the physical sciences, the use of PDEs as governing equations is widespread. Many fields, including those outside the physical sciences, use these equations to model systems and solve problems whose solutions we take for granted today, ranging from fluid mechanics to ecology.

@@

PyTorch specifically, was originally developed by Meta AI as an open source project. Today it is part of the Linux Foundation \autocite{jimzemlinWelcomingPyTorchLinux2022}. As one of the most successful and important machine learning software project, PyTorch has a big community which provides support. The PyTorch ecosystem of other projects built around PyTorch, such as torchdiffeq \autocite{Chen_torchdiffeq_2021}, are part of what makes PyTorch an appealing choice when undertaking a Machine Learning project. At its core, PyTorch provides an implementation of tensors which are generalizations of matrices for arbitrary dimensions. The tensors are surrounded by operations that are related to its manipulation and use, such as matrix multiplications or even linear solvers. In addition, PyTorch also provides many of the tools for working with Neural Networks. Other parts of PyTorch deal with the data and preprocessing, such as a way to randomly sample data or the family of operations surrounding FFTs. The features and all other benefits of both Python and PyTorch, allow for rapid prototyping and is conducive to research projects. The community means help is also not far away.
% Mean Squared Error (MSE & RMSE)
% Mean Absolute Error (MAE)
% Coefficient of Determination (R\textsuperscript{2})
% Symmetric Mean Absolute Percentage Error (sMAPE)

>>>>

% !TEX root = ./skripsi.tex
\chapter{LITERATURE REVIEW}\label{sec:literature_review}
% \noindent Bab ini mengulas secara rinci konsep-konsep dasar yang berkaitan dengn pekerjaan penelitian TA dan deskripsi studi pustaka yang dilakukan. Judul bab tidak harus seperti yang dituliskan, melainkan dapat lebih fleksibel yang mencerminkan isi paparan pada bab ini. Demikian halnya dengan judul sub bab.
\begin{figure}[H]
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
  \centering
    \tikzfig{figures/literature_map}
  \end{adjustwidth}
  \caption{Literature Map}\label{fig:literature_map}
\end{figure}
The topics this literature review will cover in this chapter is shown in \lccref{fig:literature_map}. There are four main topics which are governing equations, Fourier transform and series, machine learning regression, and relevant works to this study. These topics will be discussed in the following sections.
\section{Governing Equations}
\noindent Mathematical expressions that describe the behavior of a system are called governing equations. Typically, governing equations are in the form of Differential Equations (DE). For some systems with several variables, the governing equations are Partial Differential Equations (PDE). These equations are the foundation of many engineering and scientific models \autocite{olverIntroductionPartialDifferential2014,andersonGoverningEquationsFluid1992}. In the physical sciences, the use of PDEs as governing equations is widespread. Many fields, including those outside the physical sciences, use these equations to model systems and solve problems whose solutions we take for granted today, ranging from fluid mechanics to ecology.

@@

PyTorch specifically, was originally developed by Meta AI as an open source project. Today it is part of the Linux Foundation \autocite{jimzemlinWelcomingPyTorchLinux2022}. As one of the most successful and important machine learning software project, PyTorch has a big community which provides support. The PyTorch ecosystem of other projects built around PyTorch, such as torchdiffeq \autocite{Chen_torchdiffeq_2021}, are part of what makes PyTorch an appealing choice when undertaking a Machine Learning project. At its core, PyTorch provides an implementation of tensors which are generalizations of matrices for arbitrary dimensions. The tensors are surrounded by operations that are related to its manipulation and use, such as matrix multiplications or even linear solvers. In addition, PyTorch also provides many of the tools for working with Neural Networks. Other parts of PyTorch deal with the data and preprocessing, such as a way to randomly sample data or the family of operations surrounding FFTs. The features and all other benefits of both Python and PyTorch, allow for rapid prototyping and is conducive to research projects.
